\textbf{A Continuous Correlation Function Estimator for Large-Scale Structure}

### 2019-03-18 paper/paper.tex
update abstract

\title{A Vectorized Correlation Function Estimator For Large-Scale Structure}
%\title{A Generalized Correlation Function Estimator for Galaxy Surveys}

%Tensorial estimator?
%Generalized estimator?
%Tensorial estimator? 
%Projected estimator?
%Continuous estimator?
%Vecstimator?

@@

\begin{abstract}\noindent
% Context
The two-point correlation function (2PCF) is the most important statistic in structure formation.
However, current estimators of the 2PCF have significant limitations.
The standard Landy-Szalay (LS) estimator evaluates the 2PCF in bins of radial separation between objects, and the choice of bins introduces a trade-off between bias and variance.
Further binning trade-offs are required to determine the dependence of clustering on galaxy properties or redshift.
% Aims
We present a new, vectorized estimator (Foo) for the 2PCF that obviates binning in separation or anything else.
Instead of estimating the 2PCF in bins, it estimates the parameters of a continuous-function representation of the 2PCF in the form of a linear superposition of basis functions.
% Methods
Inspired by linear least-squares fitting, the Foo estimator marks the numerator terms of LS with vectors of basis functions of pair properties, and the denominator with a tensor of outer products of those functions.
The function estimates the best-fit linear combination of basis functions to describe the 2PCF, in the same limit in which LS is justifiably optimal for binned applications.
% Results
We apply Foo to artificial data to demonstrate that it can determine the clustering in a representation that provides more accuracy with fewer basis functions than LS, thus reducing requirements on mocks for covariance estimation.
We apply Foo to the Main Sample of the Sloan Digital Sky Survey (SDSS) to show that Foo can measure the luminosity-dependence of clustering without binning samples in luminosity.
We apply Foo to the Luminous Red Galaxy Sample of SDSS-III (DO WE?) to show that Foo can extract a small set of Fisher-optimal statistics for measuring the location of the Baryon Acoustic Feature.
We discuss other applications and limitations of Foo for present and future studies of large-scale structure; in principle it can be used to unify real-space and Fourier-space approaches because it can be used to estimate parameters for any wavelet or Fourier basis.
\end{abstract}

>>>>

\title{\textbf{A Continuous Correlation Function Estimator for Large-Scale Structure}}
%\title{\textbf{A Continuous Representation of the Correlation Function Estimator for Large-Scale Structure}}
%\title{\textbf{Correlation Function Estimation with Continuous Functions for Large-Scale Structure}}
%\title{\textbf{Estimating the Two-Point Correlation Function with Continuous Functions}}
%\title{\textbf{Projecting Two-Point Correlations onto General Basis Functions: A New Estimator For Large-Scale Structure}}
%\title{\textbf{A Correlation Function Estimator with General Basis Functions for Large-Scale Structure}}
%\title{\textbf{A Generalized Correlation Function Estimator For Large-Scale Structure}}
%\title{\textbf{No More Bins:\\ A Vectorized Correlation Function Estimator For Large-Scale Structure}}
%\title{A Generalized Correlation Function Estimator for Galaxy Surveys}

%Tensorial estimator?
%Generalized estimator?
%Tensorial estimator? 
%Projected estimator?
%Continuous estimator?

@@

\begin{abstract}\noindent
% Context
The two-point correlation function (2PCF) is the most important statistic in structure formation.
Current estimators of the 2PCF, which characterizes the clustering of density field tracers, have significant limitations.
The standard Landy-Szalay (LS) estimator evaluates the 2PCF in bins of radial separation between objects, and the choice of bins introduces a trade-off between bias and variance.
% Aims
We present a new, generalized estimator (Foo) for the 2PCF that obviates binning in separation or any other property.
% Results
The Foo estimator replaces the binned pair counts of LS with a continuous-function representation in the form of a linear superposition of basis functions.
These functions can take advantage of the known form of the 2PCF, and can depend on other properties of the pairs in addition to their separation.
Inspired by linear least-squares fitting, Foo marks the numerator terms of LS with vectors of these functions, and the denominator with a tensor of their outer products.
The estimator outputs the best-fit linear combination of basis functions to describe the 2PCF, in the same limit in which LS is justifiably optimal for binned applications. 
% Results
We apply Foo to the Luminous Red Galaxy Sample of the Sloan Digital Sky Survey (SDSS) to show that it estimates the clustering in a representation that provides more accuracy with fewer basis functions than LS, thus reducing requirements on mocks for covariance estimation.
We demonstrate that Foo can extract a compact set of Fisher-optimal statistics for measuring the location of the baryon acoustic feature.
We discuss other applications and limitations of Foo for present and future studies of large-scale structure; it could be used to determine the dependence of clustering on galaxy properties such as luminosity, and in principle it could unify real-space and Fourier-space approaches because by using a Fourier basis representation.
\end{abstract}
